\thetitle

### 2020-12-28 paper/paper.tex
simulation setup. todo: algorithm setup

@@

\subsection{Proof-of-Concept}
\label{subsec:Proof-of-Concept}

Reconsider the task depicted in Figure~\ref{fig:three-states}. The Blackwell-optimal MDP
\(\pol_{A}\), that is the one that chooses the A-loop, is shown on the left side of
Figure~\ref{fig:three-states2}. Recall that the bias values for \(\pol_{A}\) are
\(V^{\pol_{A}}(0)=-0.5\), \(V^{\pol_{A}}(1)=0.5\) and \(V^{\pol_{A}}(2)=1.5\). Our model-based
implementation infers the values \(\avgrew^{\pol_{A}} = 1\), \(V^{\pol_{A}}(0)=-0.5\), \(V^{\pol_{A}}(1)=0.5\)
and \(V^{\pol_{A}}(2)=1.4391\) fully automatically in \(200k\) steps. Furthermore, the addition of
\(V^{\pol_{A}}(2) + \Psi^{\pol_{A}}_{V}(2) = 1.4998\), where \(\Psi^{\pol_{A}}_{V}(2)\) is the exponentially
smoothed deviation for state \(2\). Thus the model-based algorithm is able to correctly approximate
the mathematical solution.

The right side of Figure~\ref{fig:three-states2} shows the same MDP for the model-free version. In
model-free reinforcement learning state-action pairs as opposed to state values are estimated. Thus
each state is replicated as often, as actions are available in that state. Therefore, state \(1\) is
replaced by states-action pairs \((1,l)\) and \((1,r)\) for moving to the left (taking the A-loop)
and to the right respectively. The dashed line indicates that these states are connected and thus
the agent has to choose among them when reaching either. In this case the inferred bias values are
\(V^{\pol_{A}}(0,r) = -0.5\), \(V^{\pol_{A}}(1,l)=V^{\pol_{A}}(1,r)=0.5\), and \(V^{\pol_{A}}(2,l)=1.5\). The above given tabular model-free
average reward reinforcement learning algorithm is able to exactly infer these values in less than
100k steps. This provides evidence that the algorithm in general infers correct solutions in regard to
the underlying constraints.

% \MS{Occasionally we write \(V^{\pol_{A}}(s)\) and $V_{\gamma}$ instead of \(V^{\pol}(s)\) and
% \(V^{\pol}_{\gamma}\) when the policy is clear from the context.}

Furthermore, in the later case \(V^{\pol_{A}}(1,l)=V^{\pol_{A}}(1,r)=0.5\), that is if the agent
resides in state \(1\) it has to choose among the both available actions. This cannot be done on
basis of the average reward, nor on the bias values. Therefore, it infers the slopes of the error
terms using the difference of the discounted state values \(V^{\pol_{A}}_{\gamma_{1}}(1,l) = 5.56\)
and \(V^{\pol_{A}}_{\gamma_{0}}(1,l) = 2.67\) for state-action pair \((1,l)\) and
\(V^{\pol_{A}}_{\gamma_{1}}(1,r) = 5.16\) and \(V^{\pol_{A}}_{\gamma_{0}}(1,r) = 1.67\) for
\((1,r)\), yielding \(\Delta V^{\pol_{A}}_\gamma(1,l) = -2.89\) and
\(\Delta V^{\pol_{A}}_\gamma(1,r) = -3.49\), where \(\gamma_{0} = 0.5\) and \(\gamma_{1}=0.8\).

The idea is that rewards are collected as soon as possible, thus the error term has to be maximised
when \(\gamma \to 1\). As we have
\(2.5 = \frac{\avgrew^{\pol_{A}}}{1-\gamma_{0}} + V^{\pol_{A}}(1,a) < V^{\pol_{A}}_{\gamma_{0}}(1,l)
= 2.67\), while \(2.5 \geqslant 1.67\), we choose action \(l\) as it is the only action with
positive error term.

% Current state:                               A
% Period:                                      5000
% Alpha:                                       0.0050
% Beta:                                        0.0700
% Delta:                                       0.0700
% Gamma:                                       0.0700
% Epsilon:                                     1.2913
% Exploration:                                 0.8609
% Algorithm:                                   BORL with gammas  (0.5,0.8); state values for rho; Deciding on V
% Zeta (for forcing V instead of W):           1.0000
% Xi (ratio of W error forcing to V):          0.2000
% Scaling (V,W,R0,R1) by V Config:             Tabular representation (no scaling needed)
% Psi Rho/Psi V/Psi W:                         (0.0000,0.0000,0.0000)
% Rho:                                         1.0000
% V                                       W
% [+0.0000]right: -0.5000                 [+0.0000]right: 0.2061
% [+1.0000]left : 0.5000                  [+1.0000]left : -0.2939
% [+1.0000]right: 0.5000                  [+1.0000]right: -2.2939
% [+2.0000]left : 1.5000                  [+2.0000]left : -1.7939
% R0                                      R1
% [+0.0000]right: 1.3333                  [+0.0000]right: 4.4444
% [+1.0000]left : 2.6667                  [+1.0000]left : 5.5556
% [+1.0000]right: 1.6667                  [+1.0000]right: 5.1556
% [+2.0000]left : 3.3333                  [+2.0000]left : 6.4444
% PsiV
% [+0.0000]right: -0.0000
% [+1.0000]left : -0.0000
% [+1.0000]right: -0.0000
% [+2.0000]left : -0.0000

    % Edges
    \path[thin, ->, bend right, >=stealth] (1) edge[above] node {\footnotesize\(2\)} (0);
    \path[thin, ->, bend right, >=stealth] (2) edge[above] node {\footnotesize\(2\)} (1);
    \path[thin, ->, bend right, >=stealth] (0) edge[below] node {\footnotesize\(0\)} (1);
    % \path[thin, ->, bend right, >=stealth] (1) edge[below] node {\footnotesize\(0\)} (2);

    \draw (6,0) node(B0) [circle,draw,minimum size=25] {\footnotesize \((0,r)\)};
    \draw (9,1.0)  node(B1l) [circle,draw,minimum size=25] {\footnotesize \((1,l)\)};
    \draw (9,-1.0)  node(B1r) [circle,draw,minimum size=25] {\footnotesize \((1,r)\)};
    \draw (12,0)  node(B2) [circle,draw,minimum size=25] {\footnotesize \((2,l)\)};

    \path[thin, ->, bend right, >=stealth] (B1l) edge[above] node {\footnotesize\(2\)} (B0);
    \path[thin, ->, bend right, >=stealth] (B2) edge[above] node {\footnotesize\(2\)} (B1l);
    \path[thin, ->, bend right, >=stealth] (B0) edge[below] node {\footnotesize\(0\)} (B1l);
    \path[thin, ->, bend right, >=stealth] (B1r) edge[below] node {\footnotesize\(0\)} (B2);

    \path[thin, dashed] (B1r.west) edge[below] node {} (B1l.west);
    \path[thin, dashed] (B1r.east) edge[below] node {} (B1l.east);

  \end{tikzpicture}
  \caption{\label{fig:three-states2} The left side depicts the Blackwell-optimal MDP of
    Figure~\ref{fig:three-states}, that is the MDP that takes the A loop. On the right side is the
    model-free version of the same MDP with policy \(\pol_{A}\). As in the model-free scenario
    state-action pairs are evaluated state \(1\) is split into a state that takes the left loop
    and one that traverses to the right. They are linked with dashed lines to indicate that these
    states are connected and the agent has to decide for one among them. The bias values for the
    model-free version are \(V^{\pol_{A}}(0,r) = -0.5\),
    \(V^{\pol_{A}}(1,l)=V^{\pol_{A}}(1,r)=0.5\), and \(V^{\pol_{A}}(2,l)=1.5\).}
\end{figure}

@@

This section introduces the simulation model and the parameterisation of the algorithm. To be able
to compare the performance of the algorithm we chose to implement the same setup as has been used by
\cite{SchneckenreitherHaeussler2019}.

@@

\begin{figure*}[t!]
  \centering
  \input{productionsystem}                      % Figure production system
  \caption{Production system of the simulation model with routing, processing time distributions and
    demand.} \label{fig:ps}
\end{figure*}

Therefore, we use the hypothetical flow shop make-to-order manufacturing system similar to the
system analyzed by \cite{Lee1997} and later by \cite{Schneckenreither2019}. The simulation model
consists of three work centres; each consists of a single machine and can process only one order at
a time. Figure~\ref{fig:ps} depicts the make-to-order production system setup.
%
The number of orders arriving is uniformly distributed between 3 and 15 order per period and
thus with a mean of 9 order per period.
%
% Orders arrive
% uniformly between 3 and 15 orders per period and thus a mean of 9 orders per period, or
In other words, on average every $0.11$ periods one order arrives in the order pool.
%
Incoming orders are queued at the order pool until released. The due date slack ($\DDS$), that is
the periods until incoming orders are due, is set to 7 periods.
%
Once orders are released they are queued at each work center and wait until being processed by the
machine. The queuing priority is first-come-first-serve. No preemptions are allowed. Order
routings are deterministic and embrace two production stages with diverging shape and no return
visits. This results in 2 different products. The operation times of the work centres are
uniformly distributed, cf. Table~\ref{tbl:costs}. These characteristics lead to a utilization rate
of 90\% for the bottleneck work center (WC3) in steady state. % Planning periods were set to 960
% minutes (16 hours).

% \begin{figure}[b!]
%   \centering
%   \def\arraystretch{1.2}          %  1 is the default, change whatever you need
%   \begin{table}[t!]
%     \centering
%     \begin{tabular}{|l||c|c|c|}
        %         \hline
        %     %         BEGIN RECEIVE ORGTBL optime
        %         Work Center & WC1 & WC2 & WC3\\
        %         \hline
        %         Operation time & \(\mathcal{U}(70,130)\) & \(\mathcal{U}(130,170)\) & \(\mathcal{U}(180,200)\)\\
        %     %         END RECEIVE ORGTBL optime
        %         \hline
        %       \end{tabular}
        %   %       \egroup

        %         \caption{\label{tab:OTs}Operation times.}
        %   %       \end{figure}
        %         \end{table}
\begin{table}[t]
  \centering
  \begin{tabular}{|l||c|c|c|}
    % BEGIN RECEIVE ORGTBL values
    \hline
    Work Center & WC1 & WC2 & WC3\\
    \hline
    Operation time & \(\mathcal{U}(70,130)\) & \(\mathcal{U}(130,170)\) & \(\mathcal{U}(180,200)\)\\
    % END RECEIVE ORGTBL optime
    \hline
    \multicolumn{4}{c}{}\\
    \hline
    Cost & Wc p. Order/Period & Fc p. Order/Period & Bc p. Order/Period \\
    \hline
    Value & 3 & 10 & 20 \\
    \hline
    % END RECEIVE ORGTBL values
  \end{tabular}

  \caption{\label{tbl:costs}Operation times (upper half) and costs setup (in monetary unit).}
\end{table}

        %         \begin{figure}[b!]
        %         \centering
        %         \def\arraystretch{1.2}          %  1 is the default, change whatever you need
        %         \setlength\tabcolsep{1.7pt}
        %         \begin{tabular}{|l||c|c|c|c|c|c|}

        %       \end{tabular}
        %         \egroup
        %         \caption{Operation times.}
        %         \label{tab:OTs}
        %         \end{figure}

To evaluate the performance of the different order release models we define
following performance measures similar to literature
(e.g.,~\citealt{Baykasoglu2011,Thuerer2012}):
\begin{itemize}
\item \textbf{Cost related measures:} average total holding costs for  WIP and finished goods inventory,
  costs for backorders. There are no earnings,
  thus the algorithms minimizes the costs. The setup for the actual values of the costs is given in
  Table~\ref{tbl:costs} and shows that late deliveries are especially expensive. All costs are per
  order and period, and are measured and reported at the end of each period.

  % \begin{table}[t]
  %   \centering
  %   \begin{tabular}{|l||c|c|c|}
  %     %     BEGIN RECEIVE ORGTBL values
        %         \hline
        %         Work Center & WC1 & WC2 & WC3\\
        %         \hline
        %         Operation time & \(\mathcal{U}(70,130)\) & \(\mathcal{U}(130,170)\) & \(\mathcal{U}(180,200)\)\\
        %     %         END RECEIVE ORGTBL optime
        %         \hline
        %         \multicolumn{4}{c}{}\\
        %         \hline
        %         Cost & Wc p. Order/Period & Fc p. Order/Period & Bc p. Order/Period \\
        %         \hline
        %         Value & 3 & 10 & 20 \\
        %         \hline
        %     %         END RECEIVE ORGTBL values
        %       \end{tabular}

        %         \caption{\label{tbl:costs}Operation times and costs setup (in monetary unit).}
        %         \end{table}

        %         \SH{The costs were set as follows: $Wc:Fc:Bc = 1:1.5:2.5$?}
\item \textbf{Delivery related measures:} % mean service level -- percentage of
        %         orders on time (\%SL),
  mean tardiness of late orders (TA), standard deviation of
  lateness ($\sigma$TA).
\item \textbf{Flow time related measures:} mean shop floor throughput time (time
  duration from release until entry of finished goods inventory; SFTT).
\end{itemize}

The length of each simulation run to evaluate the performance was 6000 periods including a warm-up
period of 1000 periods. Welch’s procedure was applied to approximate the length of the warm-up
period (see~\citealt{law:simulationc}).

        %         Each order release method was evaluated on 25 predefined demand
        %         streams.

        %         \MS{TODO}
\subsection{Conventional Order Release Rules}

As external benchmark for comparison we use
        %         use two different order release rules. First, we use immediate release which releases orders as
        %         soon as they arrive at the order pool. And second, we
different parameterized backward infinite loading (\BIL{}) techniques:

\begin{equation*}
  RD_{j} = DD_{j} - LT_{j} \tcom
  \label{eq:BIL}
\end{equation*}

where the release date \(RD_{j}\) of product type \(j\) is calculated by the difference of the due
date \(DD_{j}\) and the lead time \(LT_{j}\). Note that we set lead times for each product type and
not for every order as done by \cite{Ackerman1963}.

        %         The
        %         variants are named according to the used lead time $LT$. For example in case of $\BILOne$ we have
        %         $LT=1$. \MS{@Equation 1: Use LT$_{j}$ or LT?}

        %         \MS[t]{do we?}

>>>>

\usepackage{lineno}

@@

@@

This section introduces the simulation model and the parameterisation of the algorithm. To provide a
proof-of-concept for the proposed algorithm we adapt the flow shop presented in
\citet{schneckenreither2020order}. However, our algorithms operates on discrete lead times on a
product type basis and thus is not directly comparable to their order based lead time management
approach. Nonetheless, this section is largely based on the corresponding section of
\citet{schneckenreither2020order}.

@@

We adapt the simulation model of a make-to-order (MTO) flow shop with six different
products and six work-centers of \citet{schneckenreither2020order} and examine the system under
moderate and high utilisation in combination with moderate or high variability in demand and
processing times. This section provides the details of the simulation model and the experimental
setup.

% \subsection{Make-To-Order Flow Shop}
% \label{subsec:make-to-order_flow_shop}
% \subsection{Simulation model}
% \label{subsec:Simulation_model}

The simulation model is depicted in Figure~\ref{fig:ps}, where the customers initiate the process by
placing orders as indicated by the dashed line.
%
\begin{figure*}[t!]
  \centering
  \input{figures/productionsystem}                      % Figure production system
  \caption{Production System of the Simulation Model with routing, processing time distributions and
    demand interarrival time distributions.} \label{fig:ps}
\end{figure*}
%
%
The manufacturer produces six different product types, each of which is identified by a natural
number ${1,2,\ldots,6}$ and has a different routing through the production system. The routing setup
is provided by corresponding labels of the edges. For instance, product types $1-3$ are routed from
machine $M1$ to machine $M2$, while the other products are transferred to machine $M3$. The
production system consists of three production stages with diverging material flow and no return
visits.
%
The incoming orders are uniformly distributed among the product types.
%
A period lasts $960$ minutes ($=16$ hours) which represent two \(8\)-hour shifts. At the
beginning of each period orders can be released into the production system assuming material
availability for all orders at their release date. Upon release, the orders are
placed in the buffer at machine $M1$. Buffers and inventories are plotted as filled squares. Thus,
each workstation is equipped with a buffer which queues the orders until processing is started. All
buffers use a first-come-first-serve dispatching rule.
%
Furthermore, each workstation processes only one order at a time and early deliveries are
prohibited. Orders completed ahead of their due date remain in the finished goods inventory (\fgi{})
until they are due and sent to the customer.

\paragraph{Processing Times.} The machine processing time distributions are given under the
corresponding node labels of the machines. To simulate high or moderate variance the processing
times for all machines are  drawn from an exponential or an uniform distribution,
respectively. There is one bottleneck machine ($M5$) and therefore we refer to product
types $2$ and $5$, those routed through machine $M5$, as
bottleneck products whereas products $1,3,4,6$ are non-bottleneck products.

\paragraph{Demand.} The incoming orders are placed in the order pool with a due date slack of
\dds{} periods, that is each order arriving within period $t$ will be due at the end of period
$t+\dds{}$. The due date slack of \(\dds{}\) was chosen to (i) ensure sufficient time between the
first occurrence of orders in the order pool and the latest possible release of orders and (ii) to
have a clear cause and effect relationship between the order release decision and the cost
performance in the analysis.
%
To simulate high and moderate variability of the demand process the interarrival time between
consecutive incoming orders is either drawn from an exponential ($\Exp$) or an uniform ($\Unif$)
distribution, which are adjusted to yield the desired bottleneck utilisation level of either $70\%$
with $\Exp(135)$ and $\Unif(95,175)$, or $80\%$ with $\Exp(118)$ and $\Unif(78,158)$. These values
were chosen as they comprise the non-linear relationship between flow times and high utilisation
levels.

\paragraph{Order Release.}
%
Before the order release decision is made, all orders in the order pool are sorted by due date. This
portrays the implementation of a sequencing rule. According to this sequence, orders are considered
for release in the beginning of each period starting with the highest priority order.

In our model, orders are released by specifying lead times
$\lt_{1}, \lt_{2}, \ldots, \lt_{6} \geqslant 1$, where the index corresponds to the product type and
$\lt_{i} \in \mathbb{N}$.
%
%
By setting a lead time $\lt_{i}$ a \emph{planned release date} is computed for each
order $j$ of product type $i$ in the order pool given by
%
\begin{linenomath*}
  \begin{equation}
    \prd{}_j= \dd{}_j - \lt_{i}\ ,
    \label{eq:Orel}
  \end{equation}
\end{linenomath*}

where $\dd_{j}$ denotes the due date of the order.  For dynamic order releases the lead times
$\lt_{i}$ may vary from period to period, whereas in static order release methods the lead times are
predetermined and fixed (\citealt{RagatzMabert1988,KimBobrowski1995}).
%
For both approaches a job of product type $i$ with lead time $\lt{}_{i}$ in period $t$ and due date
$\dd_{j}$ is released at the end of period $t$ if and only if $t \geqslant \prd{}_{j}$.
%
Thus, in the dynamic setting  the planned
release date $\prd{}_{j}$ of order $j$ can be updated several times before it is actually released
to the production system.
%
However, once an order is released its release cannot be revoked.
%
% If there are several orders with the same due date the order release
% sequence is randomized.
%
Hence, if the set lead time corresponds with the actual flow time the product is finished in the
same period as it is shipped. If the lead times are set either too long or short,
the order has to wait in the \fgi{} until it is due or the order is late and backorder (BO) costs
occur.

\paragraph{Costs.}
%
The cost parameters are set by assuming an increase in value from raw material ($1$~Dollar per order
and period) to the final product ($4$~Dollar per order and period) and the backorder costs are set
very high ($16$~Dollar per order and period) due to the MTO environment. All costs are assessed
based on the production system state at the end of each period.

\subsection{Conventional Order Release Rules}

As external benchmark for comparison we use different parameterized backward infinite loading
(\BIL{}) techniques \citep{Ackerman1963}. \BIL{} uses Equation~\ref{eq:Orel} with a predetermined
and fixed lead times \(\lt_{i}\).
%
% \begin{equation*}
%   \rd_{j} = \dd_{j} - \lt_{j} \tcom
%   \label{eq:BIL}
% \end{equation*}
%
% where the release date \(RD_{j}\) of product type \(j\) is calculated by the difference of the due
% date \(DD_{j}\) and the lead time \(LT_{j}\).
Note that we set lead times for each product type and not for every order as done by
\cite{Ackerman1963}.
